Storm Data Analysis - Week 4

### 2021-03-28 Manuscript.Rmd
Final, start bug checks

---
title: "Storm Data Analysis - Week 4"
author: "Marco Baciarello"
date: "3/17/2021"
output: html_document
  fig_caption: yes
---

@@

```{r figure-captions}
fig.1.caption = "**Fig. 1:** Figure 1"
```

>>>>

---
title: "Storm Data Analysis - Week 4"
author: "Marco Baciarello"
date: "3/17/2021"
output:
  html_document:
    fig_captions: TRUE

---

@@

```{r figure-captions, include=FALSE}
fig.1.caption = "**Fig. 1:** Figure 1"
```

``` {r final-data-computations}
